An Empirical Analysis of the Role of Energy in Economic Growth

### 2015-03-18 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Removed row number for full CES model.
Changed Table 2 caption.
Added a new version of the models table.
New order for CES boundary models.

\begin{table} \caption{Boundary (rows~1--20) and generic (row~21) models for the CES equation.} 
\label{tab:CES_boundary_models} 
  \begin{center}
    \begin{tabular}{r c c c c l} 
      \toprule
      & $\delta_1$  & $\sigma_1$ & $\delta$   & $\sigma$ & Boundary model \\
      \midrule
      1. & 1           & ---        & 1          & ---      & $y = \gamma A x_1$ \\
      2. & 0           & ---        & 1          & ---      & $y = \gamma A x_2$ \\
      3. & ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
%
      4. &             & $\infty$   & 1          & ---        
            & $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
%
      5. &             &            & 1          & ---
            & $y = \gamma A \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}$ \\
\midrule
      6. & ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
      7. & 1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
      8. & 0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
      9. & ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
%
     10. & 1           & ---        &            & $\infty$        
            & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
%
     11. & 0           & ---        &            & $\infty$        
            & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
%
     12. &             & $\infty$   &            & $\infty$        
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - \delta_1 \right) x_2 \right] 
                    + \left( 1 - \delta \right) x_3  \right\}$ \\
%
     13. & ---         & 0          &            & $\infty$        
            & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
%
     14. &             & $\infty$   & ---        & 0
            & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
%
     15. & 1           & ---        &         & 
            & $y = \gamma A \left[ \delta x_1^{-\rho} 
                    + \left(1 - \delta \right) x_3^{-\rho} \right] ^ {-1/\rho}$ \\ 
%
     16. & 0           & ---        &            & 
            & $y = \gamma A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right) x_3^{-\rho} \right]^{-1/\rho}$ \\
%
     17. &             & $\infty$   &            &
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 
                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}  
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\
%
     18. & ---         & 0          &            & 
            & $y = \gamma A \left\{ \delta \left[ \min \left( x_1, \, x_2 \right) \right]^{-\rho}  
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
%
     19. &             &            &            & $\infty$
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}  
                    + \left( 1 - \delta \right) x_3  \right\}$ \\ 
%
     20. &            &            & ---     & 0
            & $y = \gamma A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}, \, x_3 \right\}$ \\ 
\midrule
     21. &            &            &         & 
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/\rho_1}  
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

>>>>

\begin{table} \caption{CES boundary models (rows~1--20) and full model (bottom row). ORIGINAL.  **** DELETE EVENTUALLY ****} 
  \begin{center}
    \begin{tabular}{r c c c c l} 
      \toprule
      & $\delta_1$  & $\sigma_1$ & $\delta$   & $\sigma$ & Boundary model \\
      \midrule
      1. & 1           & ---        & 1          & ---      & $y = \gamma A x_1$ \\
      2. & 0           & ---        & 1          & ---      & $y = \gamma A x_2$ \\
      3. & ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
%
      4. &             & $\infty$   & 1          & ---        
            & $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
%
      5. &             &            & 1          & ---
            & $y = \gamma A \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}$ \\
\midrule
      6. & ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
      7. & 1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
      8. & 0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
      9. & ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
%
     10. & 1           & ---        &            & $\infty$        
            & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
%
     11. & 0           & ---        &            & $\infty$        
            & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
%
     12. &             & $\infty$   &            & $\infty$        
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - \delta_1 \right) x_2 \right] 
                    + \left( 1 - \delta \right) x_3  \right\}$ \\
%
     13. & ---         & 0          &            & $\infty$        
            & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
%
     14. &             & $\infty$   & ---        & 0
            & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
%
     15. & 1           & ---        &         & 
            & $y = \gamma A \left[ \delta x_1^{-\rho} 
                    + \left(1 - \delta \right) x_3^{-\rho} \right] ^ {-1/\rho}$ \\ 
%
     16. & 0           & ---        &            & 
            & $y = \gamma A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right) x_3^{-\rho} \right]^{-1/\rho}$ \\
%
     17. &             & $\infty$   &            &
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 
                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}  
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\
%
     18. & ---         & 0          &            & 
            & $y = \gamma A \left\{ \delta \left[ \min \left( x_1, \, x_2 \right) \right]^{-\rho}  
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
%
     19. &             &            &            & $\infty$
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}  
                    + \left( 1 - \delta \right) x_3  \right\}$ \\ 
%
     20. &            &            & ---     & 0
            & $y = \gamma A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}, \, x_3 \right\}$ \\ 
\midrule
         &            &            &         & 
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/\rho_1}  
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

\begin{table} \caption{CES boundary models (rows~1--20) and full model (bottom row). 
                       Re-ordered, but with original model numbers. **** DELETE EVENTUALLY ****}
  \begin{center}
    \begin{tabular}{r c c c c l} 
      \toprule
      & $\delta_1$  & $\sigma_1$ & $\delta$   & $\sigma$ & Boundary model \\
      \midrule
      1. & 1           & ---        & 1          & ---      & $y = \gamma A x_1$ \\
      2. & 0           & ---        & 1          & ---      & $y = \gamma A x_2$ \\
      6. & ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
      \midrule
      3. & ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
      7. & 1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
      8. & 0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
%
      4. &             & $\infty$   & 1          & ---        
            & $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
%
     10. & 1           & ---        &            & $\infty$        
            & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
%
     11. & 0           & ---        &            & $\infty$        
            & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
%
      5. &             &            & 1          & ---
            & $y = \gamma A \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}$ \\
%
     15. & 1           & ---        &         & 
            & $y = \gamma A \left[ \delta x_1^{-\rho} 
                    + \left(1 - \delta \right) x_3^{-\rho} \right] ^ {-1/\rho}$ \\ 
%
     16. & 0           & ---        &            & 
            & $y = \gamma A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right) x_3^{-\rho} \right]^{-1/\rho}$ \\
      \midrule
      9. & ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
%
     13. & ---         & 0          &            & $\infty$        
            & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
%
     14. &             & $\infty$   & ---        & 0
            & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
%
     12. &             & $\infty$   &            & $\infty$        
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - \delta_1 \right) x_2 \right] 
                    + \left( 1 - \delta \right) x_3  \right\}$ \\
%
     18. & ---         & 0          &            & 
            & $y = \gamma A \left\{ \delta \left[ \min \left( x_1, \, x_2 \right) \right]^{-\rho}  
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
%
     20. &            &            & ---     & 0
            & $y = \gamma A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}, \, x_3 \right\}$ \\ 
%
     19. &             &            &            & $\infty$
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}  
                    + \left( 1 - \delta \right) x_3  \right\}$ \\ 
%
     17. &             & $\infty$   &            &
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 
                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}  
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\
\midrule
         &            &            &         & 
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/\rho_1}  
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

\begin{table} \caption{CES boundary models (rows~1--20) and full model (bottom row).} 
\label{tab:CES_boundary_models} 
  \begin{center}
    \begin{tabular}{r c c c c l} 
      \toprule
      & $\delta_1$  & $\sigma_1$ & $\delta$   & $\sigma$ & Boundary model \\
      \midrule
      1. & 1           & ---        & 1          & ---      & $y = \gamma A x_1$ \\
      2. & 0           & ---        & 1          & ---      & $y = \gamma A x_2$ \\
      3. & ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
      \midrule
      4. & ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
      5. & 1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
      6. & 0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
%
      7. &             & $\infty$   & 1          & ---        
            & $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
%
      8. & 1           & ---        &            & $\infty$        
            & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
%
      9. & 0           & ---        &            & $\infty$        
            & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
%
     10. &             &            & 1          & ---
            & $y = \gamma A \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}$ \\
%
     11. & 1           & ---        &         & 
            & $y = \gamma A \left[ \delta x_1^{-\rho} 
                    + \left(1 - \delta \right) x_3^{-\rho} \right] ^ {-1/\rho}$ \\ 
%
     12. & 0           & ---        &            & 
            & $y = \gamma A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right) x_3^{-\rho} \right]^{-1/\rho}$ \\
      \midrule
     13. & ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
%
     14. & ---         & 0          &            & $\infty$        
            & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
%
     15. &             & $\infty$   & ---        & 0
            & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
%
     16. &             & $\infty$   &            & $\infty$        
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - \delta_1 \right) x_2 \right] 
                    + \left( 1 - \delta \right) x_3  \right\}$ \\
%
     17. & ---         & 0          &            & 
            & $y = \gamma A \left\{ \delta \left[ \min \left( x_1, \, x_2 \right) \right]^{-\rho}  
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
%
     18. &            &            & ---     & 0
            & $y = \gamma A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}, \, x_3 \right\}$ \\ 
%
     19. &             &            &            & $\infty$
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}  
                    + \left( 1 - \delta \right) x_3  \right\}$ \\ 
%
     20. &             & $\infty$   &            &
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 
                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}  
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\
\midrule
         &            &            &         & 
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/\rho_1}  
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}
